\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{palatino}

\begin{document}

\part{Adam Cunningham Kidd }

\section{Personal Profile}
I am a potterer and a tinkerer with mid level experience searching for a role that will allow me room to grow. Proven record designing and building customer focused applications. I strive to create robust, useful code.


\section{Work experience}

\begin{eventlist}

\item{July 2016 -- September 2016}
     {VHBU @ Mettler Toledo, China}
     {Summer Intern}

With an IAESTE internship I travelled to China to work with MT. This provided a unique opportunity to learn about a new country internally, especially the work norms. I completed the Customise Form Module project which allowed users to customise the layout of their HGV scale terminals. The technologies used were Windows Forms, C\#, XML and SQL. In addition to the technical side, I also helped the native staff improve their English and taught about western culture and Scotland. I worked on a HR project to improve the quality of staff meetings and was involved in many cultural exchange activities.

\item{June 2015 -- September 2015}
     {IS \& GS @ Lockheed Martin, Glasgow}
     {Summer Intern}

I worked for the Public Services, PS, department for IS \& GS LM and completed work in two projects. One system that was already live and needed accessibility tweaks for screen readers and one system that PS was due to take over from an external company and my job was creating unit tests and heavily refactoring in preparation for the switch, using C\# and .NET. In addition, I used Nhibernate, an object relational mapper for mapping domain models to relational databases, and Rhinomocks, a dynamic mock object framework for .NET to aid testing

\item{June 2014 -- October 2014}
     {Arta, Glasgow}
     {Bar Staff}

\item{June 2013 -- August 2013}
     {Dumfries House, Cumnock}
     {Event Waiting Staff}
     
\pagebreak

\item{October 2011 -- January 2012}
     {TK Maxx, Ayr}
     {Associate}


\end{eventlist}

%\personal
 %   [www.entidi.com]
  %  {viale Conciliazione, 13\newline 25039 -- Travagliato (BS)}
  %  {+39 (30) 6862332}
   % {ntd@entidi.it}

\section{Education}

\begin{school}

\item{2006 -- 2012}
     {Belmont Academy}
     {Secondary School}
     {Ayr}

\end{school}
\begin{uni}

\item{2012 -- 2017}
     {University of Strathclyde}
     {CES MEng, Computer and Electronic Systems}
     {First Year -- 73\%}
     {Second Year -- 73\%}
     {Third Year -- 70\%}
     {Fourth Year -- 69\%}
	{Fifth Year -- 71\%}
\end{uni}

\section{End of year projects}

\begin{yearlist}

\item{2016}
     {5th Year Group Project}
     {Ground Station Platform}
\end{yearlist}

Developing a Django solution to predict cube satellite locations, schedule the cubesat passes and control the dish rotators automatically. 
\\ 

\begin{yearlist}
\item{2015}
     {4th Year Individual project}
     {Secure IoT Sensor Platform}
\end{yearlist}

Created a solution to securely transfer sensor data over the internet on a low powered Arduino microcontroller. Involved the use of C, JSP, SQL and NaCl encryption library.

\section{Languages}

\begin{factlist}
\item{English}{Native speaker}
\item{Spanish}{Intermediate}
\end{factlist}

%\section{Software skills}

%\begin{factlist}

%\item{Good level}
    
     
%C, PHP, HTML, CSS, autotools, git, gcc, GTK+, GObject, shell, MS-DOS, Linux, ladder, G-Code
%\item{Intermediate}
     %{Lua, \LaTeX, MySQL, VBA, cuBasic, pascal, subversion, LabVIEW}
%	 {Java, C\#}
	 
%\item{Basic level}
    % {Windows, FreeBSD, OpenIndiana, Postgres}
%	{\LaTeX, C, Python, XML, SQL, HTML, JSP}
	
%\end{factlist}
\section{Personal Interests}

For the last three years, I've been practising Spanish and am aiming for fluency. I have a keen interesting in enthusiast grade consumer technology and I have enjoyed reading all my life.


\end{document}
