%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font
\usepackage{bookman}

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\newcommand\tab[1][1cm]{\hspace*{#1}}

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\address {Adam Cunningham Kidd \\
1/1 23 Turnbull Street \\
Glasgow, G1 5PR \\
adam\_kidd@hotmail.co.uk \\
07887383323}

\begin{letter}{} 


%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

%\begin{center}
%\large\bf Dr. John Smith \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
%123 Broadway \\ City, State 12345 \\ (000) 111-1111 % Your address and phone number
%\end{center} 
%\vfill

%\signature{Adam Kidd} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{To whom it may concern,} 
 
	I write to you today to express my interest in the advertised role of Software Developer at DeltaDNA. I currently work as a senior software developer at Leidos, based in Glasgow, and I am now looking to expand my experience.\\*
\tab	 I have worked at Leidos since 2017, where I first joined as a graduate, following the completion of a Masters in Engineering in the subject of CES at the University of Strathclyde. Since completing the two year graduate scheme, I have used the experience and knowledge gained to work up to the role of senior developer, where I have contributed to a number of successful projects through application of my skills, which include technical expertise modelling, building and testing software. I have learned a lot during my time at Leidos about how enterprise software projects function and the infrastructure that supports integration and deployment. I have a firm understanding of OO principles, experience with backend tech like .NET MVC and Web API, and frontend frameworks like VueJS.\\
\tab	I have solid testing experience from unit (with mocks) and integration to E2E. I am experienced with Git and managed the CI/CD process for a couple of projects, I maintained and improved code standards on every project through mentoring and our merge request process. My experiences on agile projects improved my ability to estimate features and helped enable the delivery of an effective product that fulfilled the user’s needs.\\
\tab	A big part of my role was to guide the customer; using workshops, user stories, use cases and mock-ups to walk them through their initial wishes to concrete requirements and encouraging them to think about all aspects of the stories to root out anything they may have missed. I dealt with the issues that arose from working with multiple different teams, and from conflicting requirements, and learned about effective customer interaction to create code that could stand up in the real world. This increased higher customer satisfaction and help us find and resolve issues at the earliest stage possible.\\
\tab	I have collaborated well in teams with different types of people, and I find it interesting learning different viewpoints and ways of working. It is a key focus of mine to help others develop as I have relied on colleagues to become an effective developer. I have been heavily involved in Leidos’ graduate apprentice scheme coaching; I am an apprentice mentor, partially responsible for developing the skillset of my mentees. I also actively participated in Leidos’ career events, such as manning stalls at University graduate fairs, and speaking to potential applicants at recruitment events. \\
\tab	I have always taken an interest in how things work, and have used this interest to gain knowledge to help me solve problems. I would like to use this drive for learning new things to broaden my expertise and assist me in becoming ever better. I have developed a great deal in the last four years but I recognise the only thing I know is that I know nothing and always look to learning. Completing certifications and attending courses such as azure fundamentals and a recent UI/UX course has allowed me to gain new insights and I look to continue this expansion of understanding. I am confident I can expand my horizons, excel in an intensive environment and provide amazing solutions at DeltaDNA.

\closing{Sincerely yours,

Adam Kidd}


%\encl{Curriculum vitae, employment form} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}